Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-29 snapshot_system/failover.tex
revised
Added new 105VM figure.

In our experiment with Alibaba data, the ratio $\sigma$ 
is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
cost.  Figure~\ref{fig:storageCDS} shows the storage cost ratio of VC and VO when 
$r$=3, and $r_c$ varies from 3 to 10.
The result shows that the storage cost for adding extra replication for PDS
is insignificant.

@@

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig:vo-links}
\end{figure}
}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=No] {figures/vo_vm_links.txt};
		\addplot table[x=VMs,y=N1] {figures/vc_vm_links.txt};
                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

in our current testbed we have measured the average number of links per chunk
(Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
(Figure~\ref{fig:fsb-links}) in our dataset. For the complete dataset, we also
found the average number of links to PDS chunks, which was \~19 using a 2\%
PDS. From Figure~\ref{fig:fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both PDS
chunks and non-PDS chunks. In the VO model all data is shared, but in VC only
the PDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each non-PDS chunk. You can see the increase in
reliability in Figure~\ref{fig:vm-availability}.
}

@@

\begin{table}
    \begin{tabular}{|l|lll|}
    \hline
    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
                                    & $R=3$ & $R=4$ & $R=5$\\
    \hline
    1           &  100      & 100       & 100\\
    2           & 100       & 100       & 100\\
    3          & 99.999     & 100       & 100\\
    5          & 99.993     & 99.9999   & 99.999998\\
    10          & 99.926    & 99.995    & 99.999\\
    20          & 99.295    & 99.876    & 99.979\\
    \hline
    \end{tabular}
    \caption{Availability in a 100 machine cluster of a single FSB with different replication factors}
    \label{tab:fsb-availability}
\end{table}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}

>>>>

In our experiment with Alibaba data, the ratio $\sigma$ 
is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
cost.  Figure~\ref{fig:storagePDS} shows the storage cost ratio of VC and VO when 
$r$=3, and $r_c$ varies from 3 to 10.
The result shows that the storage cost for adding extra replication for PDS
is insignificant.

@@

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[htbp]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig:vo-links}
\end{figure}
}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=No] {figures/vo_vm_links.txt};
		\addplot table[x=VMs,y=N1] {figures/vc_vm_links.txt};
                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
		\addplot table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

in our current testbed we have measured the average number of links per chunk
(Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
(Figure~\ref{fig:fsb-links}) in our dataset. For the complete dataset, we also
found the average number of links to PDS chunks, which was \~19 using a 2\%
PDS. From Figure~\ref{fig:fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both PDS
chunks and non-PDS chunks. In the VO model all data is shared, but in VC only
the PDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each non-PDS chunk. You can see the increase in
reliability in Figure~\ref{fig:vm-availability}.
\begin{table}
    \begin{tabular}{|l|lll|}
    \hline
    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
                                    & $R=3$ & $R=4$ & $R=5$\\
    \hline
    1           &  100      & 100       & 100\\
    2           & 100       & 100       & 100\\
    3          & 99.999     & 100       & 100\\
    5          & 99.993     & 99.9999   & 99.999998\\
    10          & 99.926    & 99.995    & 99.999\\
    20          & 99.295    & 99.876    & 99.979\\
    \hline
    \end{tabular}
    \caption{Availability in a 100 machine cluster of a single FSB with different replication factors}
    \label{tab:fsb-availability}
\end{table}

}
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}

\comments{

@@
